### 2016-02-19 paper.tex
Allow automatic float placement
Add RVAT description and wake figs; resolves #28

@@

\begin{figure}[h]
    \includegraphics[width=0.95\textwidth]{figures/strut_covers.eps}

@@

\begin{figure}[h]
    \centering

@@

\begin{table}[ht]
\centering
\begin{tabular}{c|c|c|c|c}
Tow speed (m/s) & $Re_D$ & $Re_{c_\mathrm{tip}}$ & $Re_{c_\mathrm{root}}$ & $Re_{c_\mathrm{mid}}$\\
\hline
0.4 & $4.3 \times 10^5$ & $5.0 \times 10^4$ & $8.3 \times 10^4$ & $6.6 \times 10^4$ \\
0.6 & $6.5 \times 10^5$ & $7.4 \times 10^4$ & $1.2 \times 10^5$ & $9.9 \times 10^4$ \\
0.8 & $8.6 \times 10^5$ & $9.9 \times 10^4$ & $1.7 \times 10^5$ & $1.3 \times 10^5$ \\
1.0 & $1.1 \times 10^6$ & $1.2 \times 10^5$ & $2.1 \times 10^5$ & $1.7 \times 10^5$ \\
1.2 & $1.3 \times 10^6$ & $1.5 \times 10^5$ & $2.5 \times 10^5$ & $2.0 \times 10^5$ \\
\end{tabular}

@@

\begin{figure}[h]
    \includegraphics[width=\textwidth]{figures/turbine_coordinate_system.eps}

@@

\begin{figure}[h]
    \includegraphics[width=\textwidth]{figures/cp_curves.eps}

@@

\begin{figure}[h]
    \includegraphics[width=\textwidth]{figures/cd_curves.eps}

@@

\begin{figure}[h]
    \includegraphics[width=\textwidth]{figures/perf_re_dep.eps}

@@

\begin{figure}[ht!]
    \includegraphics[width=\textwidth]{figures/perf_covers.eps}

@@

\begin{figure}[ht!]
    \includegraphics[width=\textwidth]{figures/no_blades_all.eps}

@@

The mean velocity field at the chosen optimal tip speed ratio $\lambda_0=3.1$, 1
m downstream ($x/D=0.93$) is plotted in Fig.~\ref{fig:meancontquiv}. The mean
streamwise velocity deficit is markedly more symmetric than that of the
UNH-RVAT, with lower acceleration around the turbine due to the lower rotor drag
coefficient and a slightly blockage ratio \cite{Bachant2015-JoT}. Tip vortex
shedding is relatively weaker, which is likely an effect of the RM2's smaller
blade chord length and tapered blades.

\begin{figure}[h]
    \includegraphics[width=\textwidth]{figures/meancontquiv.eps}

    \caption{{\bf Mean Velocity.} Mean velocity field (looking upstream) at 1 m
    downstream ($x/D=0.93$), $U_\infty=1.0$ m/s, and $\lambda=3.1$. Refer to
    Fig.~\ref{fig:coordinates} for turbine axis orientation. Solid dark gray
    lines indicate turbine frontal area.}

@@

Fig.~\ref{fig:kcont} shows the turbulence kinetic energy in the turbine wake. We
mainly see unsteadiness in the flow generated by the blade tip vortex shedding
(the horizontal band around $z/H=0.5$). Compared with the UNH-RVAT, turbulence
generation is lower overall, without the intense vertical band around $y/R=-1$,
which indicates that the RM2 blades are operating further from
stall---consistent with its higher optimal tip speed ratio.

\begin{figure}[h]
    \includegraphics[width=\textwidth]{figures/k_contours.eps}

    \caption{{\bf Turbulence Kinetic Energy.} Turbulence kinetic energy (looking
    upstream) at 1 m downstream ($x/D=0.93$), $U_\infty=1.0$ m/s, and
    $\lambda=3.1$. Solid black lines indicate turbine frontal area.}

@@

\begin{figure}[ht!]
    \includegraphics[width=0.9\textwidth]{figures/K_trans_bar_graph.eps}

>>>>

The UNH-RVAT, for which the performance, near-wake, and Reynolds number
dependence of was investigated using the same experimental setup as the study
here \cite{Bachant2015-JoT, Bachant2016-Energies}, was an H-rotor of 1 m height
and 1 m diameter. The UNH-RVAT experimental datasets are also openly available
\cite{Bachant2014-RVAT-baseline, Bachant2016-RVAT-Re-dep}, and provide an
interesting comparison for the near-wake dynamics of a rotor similar in scale to
the 1:6 RM2, but with non-tapered blades and a high solidity $c/R = 0.28$.

@@

\begin{figure}
    \includegraphics[width=0.95\textwidth]{figures/strut_covers.eps}

@@

\begin{figure}
    \centering

@@

\begin{table}
\centering
\begin{tabular}{c|c|c|c|c}
Tow speed (m/s) & $Re_D$ & $Re_{c_\mathrm{tip}}$ & $Re_{c_\mathrm{root}}$ & $Re_{c_\mathrm{mid}}$\\
\hline
0.4 & $4.3 \times 10^5$ & $5.0 \times 10^4$ & $8.3 \times 10^4$ & $6.6 \times 10^4$ \\
0.6 & $6.5 \times 10^5$ & $7.4 \times 10^4$ & $1.2 \times 10^5$ & $9.9 \times 10^4$ \\
0.8 & $8.6 \times 10^5$ & $9.9 \times 10^4$ & $1.7 \times 10^5$ & $1.3 \times 10^5$ \\
1.0 & $1.1 \times 10^6$ & $1.2 \times 10^5$ & $2.1 \times 10^5$ & $1.7 \times 10^5$ \\
1.2 & $1.3 \times 10^6$ & $1.5 \times 10^5$ & $2.5 \times 10^5$ & $2.0 \times 10^5$ \\
\end{tabular}

@@

\begin{figure}
    \includegraphics[width=\textwidth]{figures/turbine_coordinate_system.eps}

@@

\begin{figure}
    \includegraphics[width=0.9\textwidth]{figures/cp_curves.eps}

@@

\begin{figure}
    \includegraphics[width=0.9\textwidth]{figures/cd_curves.eps}

@@

\begin{figure}
    \includegraphics[width=\textwidth]{figures/perf_re_dep.eps}

@@

\begin{figure}
    \includegraphics[width=\textwidth]{figures/perf_covers.eps}

@@

\begin{figure}
    \includegraphics[width=\textwidth]{figures/no_blades_all.eps}

@@

The mean velocity field at the chosen optimal tip speed ratio $\lambda_0=3.1$, 1
m downstream ($x/D=0.93$) is plotted in Fig.~\ref{fig:meancontquiv}. The mean
streamwise velocity deficit is markedly more symmetric than that of the
UNH-RVAT, shown in Fig.~\ref{fig:rvat-meancontquiv}, with the RM2 inducing lower
acceleration around the turbine due to the lower rotor drag coefficient and a
slightly lower blockage ratio \cite{Bachant2015-JoT}. Tip vortex shedding is
relatively weaker, which is likely an effect of the RM2's smaller blade chord
length and tapered blades.

\begin{figure}
    \includegraphics[width=\textwidth]{figures/RVAT-Re-dep-meancontquiv_10.eps}

    \caption{{\bf UNH-RVAT Near-Wake Mean Velocity.} UNH-RVAT near-wake mean
        velocity field (looking upstream) at 1 m downstream ($x/D=1.0$),
        $U_\infty=1.0$ m/s, and $\lambda=1.9$, from \cite{Bachant2016-Energies}.
        Solid dark gray lines indicate turbine frontal area.}

    \label{fig:rvat-meancontquiv}
\end{figure}

\begin{figure}
    \includegraphics[width=\textwidth]{figures/meancontquiv.eps}

    \caption{{\bf RM2 Near-Wake Mean Velocity.} RM2 near-wake mean velocity
        field (looking upstream) at 1 m downstream ($x/D=0.93$), $U_\infty=1.0$ m/s,
        and $\lambda=3.1$. Refer to Fig.~\ref{fig:coordinates} for turbine axis
        orientation. Solid dark gray lines indicate turbine frontal area.}

@@

Fig.~\ref{fig:kcont} shows the turbulence kinetic energy in the turbine wake. We
mainly see unsteadiness in the flow generated by the blade tip vortex shedding
(the horizontal band around $z/H=0.5$). Compared with the UNH-RVAT, shown in
Fig.~\ref{fig:rvat-kcont}, turbulence generation is lower overall, without the
intense vertical band around $y/R=-1$, which indicates that the RM2 blades are
operating further from stall---consistent with its higher optimal tip speed
ratio.

\begin{figure}
    \includegraphics[width=\textwidth]{figures/RVAT-Re-dep-k_contours_10.eps}

    \caption{{\bf UNH-RVAT Near-Wake Turbulence Kinetic Energy.} Turbulence
        kinetic energy in the UNH-RVAT's near-wake (looking upstream) at 1 m
        downstream ($x/D=1.0$), $U_\infty=1.0$ m/s, and $\lambda=1.9$, from
        \cite{Bachant2016-Energies}. Solid black lines indicate turbine frontal
        area.}

    \label{fig:rvat-kcont}
\end{figure}

\begin{figure}
    \includegraphics[width=\textwidth]{figures/k_contours.eps}

    \caption{{\bf RM2 near-wake Turbulence Kinetic Energy.} Turbulence kinetic
        energy in the RM2's near-wake (looking upstream) at 1 m downstream
        ($x/D=0.93$), $U_\infty=1.0$ m/s, and $\lambda=3.1$. Solid black lines
        indicate turbine frontal area.}

@@

\begin{figure}
    \includegraphics[width=0.9\textwidth]{figures/K_trans_bar_graph.eps}
